The Shape and Color of Politics

### 2023-09-27 chapter_2/src/slides/slides.qmd
updating slides

@@

@@

- Do these associations have systematic influences on campaign strategy?

>>>>

### Borrowing concepts from social neuroscience and psychology

- Memories:
  -  are multi-dimensional encodings of previous experiences [CITATION]
    - e.g., remember giving your first job talk
      - the layout of the room
      - the colors of the chairs
      - what the room smelled like
      - what ambient sounds were there
      - how you felt
  - affectively laden [CITATION]
  - easier retrieved when recent and/or shares multiple commonalities with current object

@@

- Do these associations have systematic influences on campaign strategy? (Study 1)
- Are these hunches correct that these colors can reliably cue partisanship? (Study 2)

@@
